---
format: morinlab-manuscript-docx
---

```{r source}
library(tidyverse)
authors <- "authors.yaml"
source("src/process_authors.R")
```

```{r process_authors}

parsed_authors <- process_authors(authors)

correspondence <- c(
  "**\\*Corresponding Author**",
  "**Dr. Ryan D. Morin**",
  "Department of Molecular Biology and Biochemistry",
  "Simon Fraser University",
  " 8888 University Dr.",
  "Burnaby, BC, Canada",
  "V5A 1S6",
  "rdmorin@sfu.ca"
)
```

# Manuscript Title {.unnumbered}

`r parsed_authors$parsed_authors`

`r parsed_authors$parsed_affiliations`

`r paste0(correspondence, collapse = "  \n")`

\newpage

## Abstract

`r parsed_authors$abstract`

\newpage

## Introduction

Introduction text goes here.

## Materials and Methods

Text for materials and methods goes here.

## Results

### Results 1

Text for results subsection 1 goes here.

### Results 2

Text for results subsection 2 goes here.

## Discussion

Text for discussion section goes here.

## Acknowledgements

`r parsed_authors$acknowledgements`

## Disclosure of Conflicts of Interest

`r parsed_authors$cois`

## Data Availability

`r parsed_authors$data_availability`

## References

::: {#refs}
:::

## Figure legends

**Figure 1. Title** Legend.

**Figure 2. Title.** Legend.
